%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer 1} % Job title
{Cox Automotive Inc} % Organization
{Draper, UT} % Location
{June 2023 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed and maintained enterprise-level security software used by hundreds of software teams across the company.}
\item {Built reporting ETL jobs leveraging Cloudwatch Events, ECS Fargate, Lambda, and more.}
\item {Developed and maintained a graph database, levering NeptuneDB, storing thousands of interconnected entities, including security vulnerabilities, software components, teams, and users, to streamline data accessibility and support security workflows.}
\item {Increased security adoption of overall company inventory at Cox Automotive from 10\% to over 45\% by creating simplified upload processes and efficient defect retrieval methods.}
\item {Designed and implemented tools that generate comprehensive security status reports for more than 7,500 software components.}
\item {Integrated security solutions with industry-leading vendors, including Veracode, NoName, and Wiz.}
\item {Enhanced the overall security workflow, improving the user experience for software teams and optimizing security practices across the organization.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Campus Core} % Organization
{Remote} % Location
{November 2024 - Current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built backend services on Azure, providing secure, scalable, and real-time access to educational resources for up to 2,000 students.}
\item {Conceptualized and developed a scalable educational platform for universities, enhancing student-advisor communications using React, React Native, Tailwind, Node.js, Azure, and MySQL.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineering Intern} % Job title
{Wavetronix} % Organization
{Salt Lake City, UT} % Location
{March 2022 - January 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed and maintained a C\# application that simulated traffic patterns, allowing users to design intersections and optimize layouts for traffic engineers.}
\item {Created a C\# application to process traffic simulation data, generating visual representations in graph form for easier data analysis and interpretation.}
\item {Contributed to improving traffic design processes by making complex simulation data more accessible and understandable to engineers.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}